Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-04-15 tex/MesnardoBarba2019.tex
edit new conclusion paragraph

\IEEEPARstart{L}{ooking} for an alternative solution to university-managed HPC clusters to run CFD simulations with our in-house software, we leveraged the public cloud provider Microsoft Azure to generate reproducible computational results.
Our reproducible workflow makes use of Docker containers to faithfully port the runtime environment our CFD application to Azure.
We used the command-line utilities Azure-CLI and Batch Shipyard to run multi-instance tasks within Docker containers on the Azure Batch platform.
Our CFD simulations ran on instances of the NC-series that feature NVDIDA K80 GPU devices and enable access to InfiniBand network.
The benchmarks showed that we could get comparable runtimes between our university-managed HPC system and Microsoft Azure.
Thanks to Microsoft Azure sponsorship, we have been able to run dozens of CFD simulations of a gliding snake's model.
The study of the three-dimensional flow around a cylinder with an anatomically accurate cross-section of the flying snake is currently ongoing; output data from these runs are being analyzed and will be published in a later paper.

>>>>

\IEEEPARstart{E}{xploring} public cloud services as an alternative (or complementary) solution to university-managed HPC clusters to run CFD simulations with our in-house software, we used Microsoft Azure to generate reproducible computational results.
Our reproducible workflow makes use of Docker containers to faithfully port the runtime environment of our CFD application to Azure,
and the command-line utilities Azure-CLI and Batch Shipyard to run multi-instance tasks within Docker containers on the Azure Batch platform.
We ran CFD simulations on instances of the NC-series that feature NVIDIA K80 GPU devices and have access to InfiniBand network.
Latency and bandwidth micro-benchmarks show that our university-managed HPC system and Microsoft Azure can produce comparable runtimes.
Thanks to a Microsoft Azure sponsorship, we were able to run dozens of CFD simulations of a gliding snake's model.
Our study of the three-dimensional flow around a cylinder with an anatomically accurate cross-section of the flying snake is currently ongoing. 
We plan to analyze the output data from these runs to be published in a later paper.
